---
title: "Multiple Linear Regression - 50 Startups"
author: "Priyanka Mhatre"
date: "February 22, 2018"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# Dataset: 50_Startups.csv has information about 50 startups and their expenses, location and profits.
# Task:    Predict the profit of a startup from features like State and expenses on RnD, Admin, Marketing. 
# Target users : Investures who want to invest in profitable startups

# Load data set
```{r}
dataset = read.csv('50_Startups.csv')
head(dataset)
summary(dataset)
```

# Handle categorical data

```{r}
dataset$State = factor( dataset$State,
                        levels = c('New York','California','Florida'),
                        labels = c(1,2,3))
head(dataset)
```

# Train test split
```{r}
library(caTools)
set.seed(123)
split = sample.split(dataset$Profit, SplitRatio = 0.8)
training_set = subset(dataset, split == TRUE)
test_set = subset(dataset, split == FALSE)
```

# Fit a multiple linear regression model

```{r}
regressor = lm(formula = Profit ~ ., #. indicates all independent variables
               data = training_set)
summary(regressor)
y_pred_all = predict(regressor, test_set)
y_pred_all
```

## Since only R.D.Spend is a statistically significant variable, lets drop all other variables and check the results.

```{r}
regressor1 = lm(formula = Profit ~ R.D.Spend,
               data = training_set)
summary(regressor1)
y_pred1 = predict(regressor1, test_set)
y_pred1
```
There is a difference in the predicted values of y if we remove all oher variables. Lets try backward elimination to see whether any other variables become statistically significant as we drop predictors one by one.

# Backward Elimination

It is better to use full dataset for this analysis to get better results.

```{r}
#colnames(dataset)
regressor = lm(formula = Profit ~ R.D.Spend + Administration + Marketing.Spend + State,
               data = dataset) 
summary(regressor)
```

Dropping State as both State2 and State 3 dummy variables have a very high p-value
```{r}
regressor = lm(formula = Profit ~ R.D.Spend + Administration + Marketing.Spend,
               data = dataset) 
summary(regressor)
```

Dropping Administration as it has a very high p-value.

```{r}
regressor = lm(formula = Profit ~ R.D.Spend + Marketing.Spend,
               data = dataset) 
summary(regressor)
```

Dropping Marketing.Spend as it has a slightly higher p-value.

```{r}
regressor = lm(formula = Profit ~ R.D.Spend,
               data = dataset) 
summary(regressor)
```